Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-03-17 paper.tex
fix at sign

The function @ndcps@ takes two arguments: a set of elements with type @T@, and an initial accumulated value of type @Set[S]@.
The @ndcps@ function iteratively returns a value of type @T@ with annotated by
\texttt{\@ cps[Set[T]]} \note{JD: Tiark, can you fix the at sign? I fixed it for the other paper, but my fix doesn't work here} that denotes the final returned value of @ndcps@ is type @Set[T]@.
The @f@ introduced by the @shift@ operator is the delimited continuation at the call-site of @ndcps@.

We add an annotation \texttt{ cps[Ans]} on the return type of the @aeval@ function.
Now, for every nondeterministic choice in the abstract interpreter, we can simply call @ndcps@ on them and write the program sequentially as a concrete interpreter.
The cache is still accumulated by the next call to @ndcps@ or @aeval@, given the fact that the abstract interpreter should always use the latest cache.

>>>>

The function @ndcps@ takes two arguments: a set of elements with type @T@, and an initial accumulated value of type @Set[S]@.
The @ndcps@ function iteratively returns a value of type @T@ with annotated by
\verb|@cps[Set[T]]| that denotes the final returned value of @ndcps@ is type @Set[T]@.
The @f@ introduced by the @shift@ operator is the delimited continuation at the call-site of @ndcps@.

We add an annotation \verb|@cps[Ans]| on the return type of the @aeval@ function.
Now, for every nondeterministic choice in the abstract interpreter, we can simply call @ndcps@ on them and write the program sequentially as a concrete interpreter.
The cache is still accumulated by the next call to @ndcps@ or @aeval@, given the fact that the abstract interpreter should always use the latest cache.
